The Astropy Project

### 2017-11-06 registry.tex
python cpl

\href{https://github.com/astropy/astroscrappy}{Astro-SCRAPPY} & Yes & \href{https://pypi.python.org/pypi/astroscrappy}{astroscrappy} & Curtis McCully & \citealt{astroscrappy} \\
\href{https://github.com/astropy/astroplan}{astroplan} & No & \href{https://pypi.python.org/pypi/astroplan}{astroplan} & Brett Morris & \citealt{astroplan_AAS}\\
\href{http://github.com/astropy/astroquery}{astroquery} & Yes & \href{https://pypi.python.org/pypi/astroquery}{astroquery} & Adam Ginsburg and Brigitta Sipocz & \citealt{astroquery}\\
\href{http://github.com/astropy/ccdproc}{ccdproc} & Yes & \href{https://pypi.python.org/pypi/ccdproc}{ccdproc} & Steven Crawford, Matt Craig, and Michael Seifert & \citealt{ccdproc}\\
\href{https://github.com/jesford/cluster-lensing}{cluster-lensing} & No & \href{https://pypi.python.org/pypi/cluster-lensing}{cluster-lensing} & Jes Ford & \citealt{clusterlensing} \\
\href{https://github.com/adrn/gala}{gala} & Yes & \href{https://pypi.python.org/pypi/astro-gala}{astro-gala} & Adrian Price-Whelan & \citealt{gala}\\
\href{https://github.com/jobovy/galpy}{galpy} & Yes & \href{https://pypi.python.org/pypi/galpy}{galpy} & Jo Bovy & \citealt{galpy}\\
\href{http://github.com/gammapy/gammapy}{gammapy} & No & \href{https://pypi.python.org/pypi/gammapy}{gammapy} & Christoph Deil & \citealt{gammapy}\\
\href{http://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey-Lian Lim & \citealt{ginga}\\
\href{https://github.com/glue-viz/glue}{Glue} & Yes & \href{https://pypi.python.org/pypi/glueviz}{glueviz} & Chris Beaumont and Thomas Robitaille & \citealt{glue}\\
\href{https://github.com/spacetelescope/gwcs}{gwcs} & No & \href{https://pypi.python.org/pypi/gwcs}{gwcs} & Nadia Dencheva & \citealt{gwcs}\\
\href{https://github.com/astropy/halotools}{Halotools} & Yes & \href{https://pypi.python.org/pypi/halotools}{halotools} & Andrew Hearin & \citealt{halotools}\\
\href{http://github.com/spacetelescope/imexam}{imexam} & No & \href{https://pypi.python.org/pypi/imexam}{imexam} & Megan Sosey & \\
\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther (hamogu) & \citealt{marxs}\\
\href{https://github.com/astropy/montage-wrapper}{montage-wrapper} & Yes & \href{https://pypi.python.org/pypi/montage-wrapper}{montage-wrapper} & Thomas Robitaille & \\
\href{https://github.com/zblz/naima}{naima} & Yes & \href{https://pypi.python.org/pypi/naima}{naima} & Victor Zabalza & \citealt{naima}\\
\href{http://github.com/astropy/photutils}{photutils} & No & \href{https://pypi.python.org/pypi/photutils}{photutils} & Larry Bradley and Brigitta Sipocz & \citealt{photutils} \\
\href{http://github.com/weaverba137/pydl}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver & \\
\href{https://github.com/olebole/python-cpl}{python-cpl} & No & \href{https://pypi.python.org/pypi/python-cpl}{python-cpl} & Ole Streicher & \\
\href{https://github.com/astrofrog/reproject}{reproject} & Yes & \href{https://pypi.python.org/pypi/reproject}{reproject} & Thomas Robitaille & \\
\href{http://github.com/sncosmo/sncosmo}{sncosmo} & Yes & \href{https://pypi.python.org/pypi/sncosmo}{sncosmo} & Kyle Barbary & \citealt{sncosmo}\\
\href{https://github.com/radio-astro-tools/spectral-cube}{spectral-cube} & Yes & \href{https://pypi.python.org/pypi/spectral-cube}{spectral-cube} & Adam Ginsburg & \citealt{spectralcube}\\
\href{http://github.com/astropy/specutils}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & Nicholas Earl, Adam Ginsburg, Steve Crawford & \\

>>>>

\href{https://github.com/astropy/astroscrappy}{Astro-SCRAPPY} & Yes & \href{https://pypi.python.org/pypi/astroscrappy}{astroscrappy} & Curtis McCully & \citealt{astroscrappy} \\
\href{https://github.com/astropy/astroplan}{astroplan} & No & \href{https://pypi.python.org/pypi/astroplan}{astroplan} & Brett Morris & \citealt{astroplan_AAS}\\
\href{http://github.com/astropy/astroquery}{astroquery} & Yes & \href{https://pypi.python.org/pypi/astroquery}{astroquery} & Adam Ginsburg and Brigitta Sipocz & \citealt{astroquery}\\
\href{http://github.com/astropy/ccdproc}{ccdproc} & Yes & \href{https://pypi.python.org/pypi/ccdproc}{ccdproc} & Steven Crawford, Matt Craig, and Michael Seifert & \citealt{ccdproc}\\
\href{https://github.com/jesford/cluster-lensing}{cluster-lensing} & No & \href{https://pypi.python.org/pypi/cluster-lensing}{cluster-lensing} & Jes Ford & \citealt{clusterlensing} \\
\href{https://github.com/adrn/gala}{gala} & Yes & \href{https://pypi.python.org/pypi/astro-gala}{astro-gala} & Adrian Price-Whelan & \citealt{gala}\\
\href{https://github.com/jobovy/galpy}{galpy} & Yes & \href{https://pypi.python.org/pypi/galpy}{galpy} & Jo Bovy & \citealt{galpy}\\
\href{http://github.com/gammapy/gammapy}{gammapy} & No & \href{https://pypi.python.org/pypi/gammapy}{gammapy} & Christoph Deil & \citealt{gammapy}\\
\href{http://github.com/ejeschke/ginga}{ginga} & Yes & \href{https://pypi.python.org/pypi/ginga}{ginga} & Eric Jeschke and Pey-Lian Lim & \citealt{ginga}\\
\href{https://github.com/glue-viz/glue}{Glue} & Yes & \href{https://pypi.python.org/pypi/glueviz}{glueviz} & Chris Beaumont and Thomas Robitaille & \citealt{glue}\\
\href{https://github.com/spacetelescope/gwcs}{gwcs} & No & \href{https://pypi.python.org/pypi/gwcs}{gwcs} & Nadia Dencheva & \citealt{gwcs}\\
\href{https://github.com/astropy/halotools}{Halotools} & Yes & \href{https://pypi.python.org/pypi/halotools}{halotools} & Andrew Hearin & \citealt{halotools}\\
\href{http://github.com/spacetelescope/imexam}{imexam} & No & \href{https://pypi.python.org/pypi/imexam}{imexam} & Megan Sosey & \\
\href{https://github.com/Chandra-MARX/marxs}{marxs} & Yes & \href{https://pypi.python.org/pypi/marxs}{marxs} & Hans Moritz Günther (hamogu) & \citealt{marxs}\\
\href{https://github.com/astropy/montage-wrapper}{montage-wrapper} & Yes & \href{https://pypi.python.org/pypi/montage-wrapper}{montage-wrapper} & Thomas Robitaille & \\
\href{https://github.com/zblz/naima}{naima} & Yes & \href{https://pypi.python.org/pypi/naima}{naima} & Victor Zabalza & \citealt{naima}\\
\href{http://github.com/astropy/photutils}{photutils} & No & \href{https://pypi.python.org/pypi/photutils}{photutils} & Larry Bradley and Brigitta Sipocz & \citealt{photutils} \\
\href{http://github.com/weaverba137/pydl}{PyDL} & No & \href{https://pypi.python.org/pypi/pydl}{pydl} & Benjamin Alan Weaver & \\
\href{https://github.com/olebole/python-cpl}{python-cpl} & No & \href{https://pypi.python.org/pypi/python-cpl}{python-cpl} & Ole Streicher & \citealt{pythoncpl}\\
\href{https://github.com/astrofrog/reproject}{reproject} & Yes & \href{https://pypi.python.org/pypi/reproject}{reproject} & Thomas Robitaille & \\
\href{http://github.com/sncosmo/sncosmo}{sncosmo} & Yes & \href{https://pypi.python.org/pypi/sncosmo}{sncosmo} & Kyle Barbary & \citealt{sncosmo}\\
\href{https://github.com/radio-astro-tools/spectral-cube}{spectral-cube} & Yes & \href{https://pypi.python.org/pypi/spectral-cube}{spectral-cube} & Adam Ginsburg & \citealt{spectralcube}\\
\href{http://github.com/astropy/specutils}{specutils} & No & \href{https://pypi.python.org/pypi/specutils}{specutils} & Nicholas Earl, Adam Ginsburg, Steve Crawford & \\
